Kids PM Summary

### 2020-04-14 merge_health_datasets.Rmd
Update PM data

---
title: "KidsAIR: merge health datasets"
author: "Ethan Walker"
date: "Started 27 March 2020, Updated 8 April 2020"
output: pdf_document
---

@@

# Load individual datasets
```{r}
at_home_pm_merged <- read_rds("Output/at_home_pm_merged.rds")
kids_med_visit <- read_rds("Output/kids_med_visit.rds")
kids_birth_infancy <- read_rds("Output/kids_birth_infancy.rds")
child_home_winter <- read_rds("Output/child_home_winter.rds")
kids_csq <- read_rds("Output/kids_csq.rds")
kids_lrti <- read_rds("Output/kids_lrti.rds")
kids_medical_records <- read_rds("Output/kids_medical_records.rds")
```

# Initial data merge - long format
```{r}
kids_med_visit <- read_rds("Output/kids_med_visit.rds") %>% 
  mutate(visit_date = med_visit_date)

health_merged1 <- kids_csq %>% 
  select(-home_id) %>% 
  mutate(visit_date = csq_date) %>% 
  full_join(kids_med_visit, by = c("area", "home", "home_winter_id", "treatment",
                                   "winter_id", "child_id_num", "visit_date")) %>% 
  select(area, home, home_winter_id, winter_id, child_id_num, visit_date,
         treatment, csq_date:med_visit_mean_temp) %>% 
  arrange(area, home, home_winter_id, winter_id, child_id_num, visit_date) %>% 
  ungroup()

child_home_winter <- read_rds("Output/child_home_winter.rds") %>% 
  select(-home_id.x, -home_id.y, -chw_symptom_free_date)

@@

kids_birth_infancy <- read_rds("Output/kids_birth_infancy.rds") %>% 
  select(-home_id)

@@

at_home_pm_merged <- read_rds("Output/at_home_pm_merged.rds")

@@

kids_medical_records <- read_rds("Output/kids_medical_records.rds") %>% 
  select(-visit_date)

@@

kids_lrti <- read_rds("Output/kids_lrti.rds") %>% 
  select(-home_id)

@@

#write_rds(health_merged6, "Output/health_data_merged.rds")
#write_csv(health_merged6, "Output/health_data_merged.csv")
```

# Merge full health data with exposure data
```{r}
exposure_analysis_data_medium <- read_rds("Output/exposure_analysis_data_medium.rds")

health_data_merged <- read_rds("Output/health_data_merged.rds")

@@

#write_rds(health_exposure_data_sampling_day, "Output/health_exposure_data_sampling_day.rds")
#write_csv(health_exposure_data_sampling_day, "Output/health_exposure_data_sampling_day.csv")

health_exposure_data_sampling_day <- read_rds("Output/health_exposure_data_sampling_day.rds")

@@

#write_csv(save_var_names, "Output/kids_data_var_names.csv")
```

>>>>

---
title: "KidsAIR: merge health datasets"
author: "Ethan Walker"
date: "Started 27 March 2020, Updated 14 April 2020"
output: pdf_document
---

@@

# Load individual datasets
```{r}
output_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")

at_home_pm_merged <- 
  read_rds(paste0(output_path, "Output/at_home_pm_merged.rds"))
kids_med_visit <- 
  read_rds(paste0(output_path, "Output/kids_med_visit.rds")) %>% 
  mutate(visit_date = med_visit_date) 
kids_birth_infancy <- 
  read_rds(paste0(output_path, "Output/kids_birth_infancy.rds")) %>% 
  select(-home_id)
child_home_winter <- 
  read_rds(paste0(output_path, "Output/child_home_winter.rds")) %>% 
  select(-home_id.x, -home_id.y, -chw_symptom_free_date)
kids_csq <- 
  read_rds(paste0(output_path, "Output/kids_csq.rds"))
kids_lrti <- 
  read_rds(paste0(output_path, "Output/kids_lrti.rds")) %>% 
  select(-home_id)
kids_medical_records <- 
  read_rds(paste0(output_path, "Output/kids_medical_records.rds")) %>% 
  select(-visit_date)
```

# Initial data merge - long format
```{r}
health_merged1 <- kids_csq %>% 
  select(-home_id) %>% 
  mutate(visit_date = csq_date) %>% 
  full_join(kids_med_visit, by = c("area", "home", "home_winter_id", "treatment",
                                   "winter_id", "child_id_num", "visit_date")) %>% 
  select(area, home, home_winter_id, winter_id, child_id_num, visit_date,
         treatment, csq_date:med_visit_mean_temp) %>% 
  arrange(area, home, home_winter_id, winter_id, child_id_num, visit_date) %>% 
  ungroup()

@@

@@

@@

@@

@@

#write_rds(health_merged6, paste0(output_path, "Output/health_data_merged.rds"))
#write_csv(health_merged6, paste0(output_path, "Output/health_data_merged.csv"))
```

# Merge full health data with exposure data
```{r}
output_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")

exposure_analysis_data_medium <- 
  read_rds(paste0(output_path, "Output/exposure_analysis_data_medium.rds"))

health_data_merged <- 
  read_rds(paste0(output_path, "Output/health_data_merged.rds"))

@@

#write_rds(health_exposure_data_sampling_day, paste0(output_path, "Output/health_exposure_data_sampling_day.rds"))
#write_csv(health_exposure_data_sampling_day, paste0(output_path, "Output/health_exposure_data_sampling_day.csv"))

health_exposure_data_sampling_day <- 
  read_rds(paste0(output_path, "Output/health_exposure_data_sampling_day.rds"))

@@

#write_csv(save_var_names, paste0(output_path, "Output/kids_data_var_names.csv"))
```

### 2020-04-14 pm_summary.Rmd
Update PM data

---
title: "Kids PM Summary"
author: "Ethan Walker"
date: "Started 22 Nov 2019, Updated 2 Feb 2020"
output: pdf_document
---

@@

```{r, message=FALSE}
library(tidyverse)
library(readr)
library(readxl)
library(knitr)
library(lubridate)
jv_palette <- c("#330099","#CC0066","#FF6633", 
                 "#0099CC", "#FF9900","#CC6633",
                  "#FF3366", "#33CC99", "#33999")
```

```{r}
# Load data
pm_clean <- read_rds("Output/pm_clean.rds")
```

# Summary stats
```{r}
pm_summary <- pm_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  #filter(pm < 500) %>% 
  mutate(pm = if_else(pm > 500, 500, pm)) %>% 
  group_by(area) %>% 
  summarize("n" = n(),
            "Mean PM" = mean(pm, na.rm = TRUE), 
            "SD PM" = sd(pm, na.rm = TRUE),
            "Min PM" = min(pm, na.rm = TRUE), 
            "25%" = quantile(pm, 0.25, na.rm = TRUE),
            "Median PM" = median(pm, na.rm = TRUE),
            "75%" = quantile(pm, 0.75, na.rm = TRUE),
            "Max PM" = max(pm, na.rm = TRUE),
            "Mean Sample Days" = mean(pm_sample_interval, na.rm = TRUE),
            "SD Sample Days" = sd(pm_sample_interval, na.rm = TRUE),
            "Mean Sample Obs" = mean(pm_total_observations, na.rm = TRUE),
            "Mean % Daily Obs" = mean(percent_daily_obs_pm, na.rm = TRUE)) %>% 
  #select(-treatment) %>% 
  t()

kable(pm_summary, 
      digits = 1, align = "c")

pm_by_day <- pm_clean %>% 
  mutate(sampling_month = month(pm_datetime_new, abbr = TRUE)) %>% 
  mutate(day_of_week = factor(day_of_week,
                                 levels = c("Monday", "Tuesday", "Wednesday", "Thursday",
                                            "Friday", "Saturday", "Sunday"),
                                 labels = c("Mon", "Tues", "Wed", "Thur", "Fri", "Sat", "Sun"))) %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  #filter(pm < 500) %>% 
  mutate(pm = if_else(pm > 500, 500, pm)) %>% 
  group_by(area, day_of_week) %>% 
  summarize("Mean PM" = mean(pm, na.rm = TRUE), 
            "SD PM" = sd(pm, na.rm = TRUE),
            "Min PM" = min(pm, na.rm = TRUE), 
            "25%" = quantile(pm, 0.25, na.rm = TRUE),
            "Median PM" = median(pm, na.rm = TRUE),
            "75%" = quantile(pm, 0.75, na.rm = TRUE),
            "Max PM" = max(pm, na.rm = TRUE))
pm_by_day
```

# Boxplots for PM by study area
```{r, fig.height=6, fig.width=5}
boxplots_kids_pm <- pm_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  filter(pm < 500) %>% 
  ggplot(aes(area, pm)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=3, color="red") +
    theme_minimal() +
    ylim(0, 500) +
    #geom_hline(yintercept = 50, color = "red", size = 1.2) +
    labs(y = expression(paste("PM"[2.5], " (", mu, g/m^3, ")"))) +
    #labs(aes(x = "", y = paste("48-hour indoor PM "[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_kids_pm
```

>>>>

---
title: "Kids PM Summary"
author: "Ethan Walker"
date: "Started 22 Nov 2019, Updated April 14 2020"
output: pdf_document
header-includes:
    - \usepackage[labelformat=empty]{caption}
---

@@

```{r, message=FALSE}
library(tidyverse)
library(readr)
library(readxl)
library(knitr)
library(lubridate)
library(kableExtra)
jv_palette <- c("#330099","#CC0066","#FF6633", 
                 "#0099CC", "#FF9900","#CC6633",
                  "#FF3366", "#33CC99", "#33999")
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", 
               "#0072B2", "#D55E00", "#CC79A7")
```

```{r}
# Load data
output_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
pm_clean <- read_rds(paste0(output_path, "Output/pm_clean.rds"))
```

```{r}
# Summary stats

pm_500 <- pm_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  mutate(pm = if_else(pm > 500, 500, pm)) %>% 
  group_by(area) %>% 
  summarize("n" = n(),
            "Mean PM" = round(mean(pm, na.rm = TRUE)), 
            "SD PM" = round(sd(pm, na.rm = TRUE)),
            "Min PM" = round(min(pm, na.rm = TRUE)), 
            "25%" = round(quantile(pm, 0.25, na.rm = TRUE)),
            "Median PM" = round(median(pm, na.rm = TRUE)),
            "75%" = round(quantile(pm, 0.75, na.rm = TRUE)),
            "Max PM" = round(max(pm, na.rm = TRUE)))

pm_2000 <- pm_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  mutate(pm = if_else(pm > 2000, 2000, pm)) %>% 
  group_by(area) %>% 
  summarize("n" = n(),
            "Mean PM" = round(mean(pm, na.rm = TRUE)), 
            "SD PM" = round(sd(pm, na.rm = TRUE)),
            "Min PM" = round(min(pm, na.rm = TRUE)), 
            "25%" = round(quantile(pm, 0.25, na.rm = TRUE)),
            "Median PM" = round(median(pm, na.rm = TRUE)),
            "75%" = round(quantile(pm, 0.75, na.rm = TRUE)),
            "Max PM" = round(max(pm, na.rm = TRUE)))

pm_summary <- pm_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  group_by(area) %>% 
  summarize("n" = n(),
            "Mean PM" = round(mean(pm, na.rm = TRUE)), 
            "SD PM" = round(sd(pm, na.rm = TRUE)),
            "Min PM" = round(min(pm, na.rm = TRUE)), 
            "25%" = round(quantile(pm, 0.25, na.rm = TRUE)),
            "Median PM" = round(median(pm, na.rm = TRUE)),
            "75%" = round(quantile(pm, 0.75, na.rm = TRUE)),
            "Max PM" = round(max(pm, na.rm = TRUE)))

full_summary <- rbind(pm_summary, pm_2000, pm_500)

kable(full_summary, 
      caption = "Kids Indoor PM2.5 (Winter 1 Placebo)") %>% 
   kable_styling() %>% 
   pack_rows("No PM2.5 Cutoff", 1, 3) %>% 
   pack_rows("PM2.5 Cutoff: 2000", 4, 6) %>% 
   pack_rows("PM2.5 Cutoff: 500", 7, 9) 
```

\clearpage

```{r}
pm_by_day <- pm_clean %>% 
  mutate(sampling_month = month(pm_datetime_new, abbr = TRUE)) %>% 
  mutate(day_of_week = factor(day_of_week,
                                 levels = c("Monday", "Tuesday", "Wednesday", "Thursday",
                                            "Friday", "Saturday", "Sunday"),
                                 labels = c("Mon", "Tues", "Wed", "Thur", "Fri", "Sat", "Sun"))) %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  group_by(area, day_of_week) %>% 
  summarize("Mean PM" = mean(pm, na.rm = TRUE), 
            "SD PM" = sd(pm, na.rm = TRUE),
            "Min PM" = min(pm, na.rm = TRUE), 
            "25%" = quantile(pm, 0.25, na.rm = TRUE),
            "Median PM" = median(pm, na.rm = TRUE),
            "75%" = quantile(pm, 0.75, na.rm = TRUE),
            "Max PM" = max(pm, na.rm = TRUE))
kable(pm_by_day, 
      caption = "Kids Indoor PM2.5 by day of week (Winter 1 Placebo)", digits = 0)
```

\clearpage

# Boxplots for PM by study area
```{r, fig.height=6, fig.width=8}
boxplots_kids_pm <- pm_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  ggplot(aes(area, pm)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=4, color="red",
                 position=position_nudge(x = -0.1, y = 0)) +
    stat_summary(aes(label=round(..y.., digits = 1)), fun.y=mean, geom="text", 
                 size=7, position=position_nudge(x = -0.35, y = 0)) +
    stat_summary(fun.y=median, geom="point", shape=16, size=4, color="blue",
                 position=position_nudge(x = 0.1, y = 0)) +
    stat_summary(aes(label=round(..y.., digits = 1)), fun.y=median, geom="text", 
                 size=7, position=position_nudge(x = 0.35, y = 0)) +
    theme_minimal() +
    #ylim(0, 500) +
    labs(y = expression(paste("PM"[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_kids_pm
```

\pagebreak

```{r, fig.height=6, fig.width=8}
boxplots_kids_pm <- pm_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  ggplot(aes(area, log(pm))) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=4, color="red",
                 position=position_nudge(x = -0.1, y = 0)) +
    stat_summary(aes(label=round(..y.., digits = 1)), fun.y=mean, geom="text", 
                 size=7, position=position_nudge(x = -0.35, y = 0)) +
    stat_summary(fun.y=median, geom="point", shape=16, size=4, color="blue",
                 position=position_nudge(x = 0.1, y = 0)) +
    stat_summary(aes(label=round(..y.., digits = 1)), fun.y=median, geom="text", 
                 size=7, position=position_nudge(x = 0.35, y = 0)) +
    theme_minimal() +
    #ylim(0, 500) +
    labs(y = expression(paste("Log PM"[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_kids_pm
```
